---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testr6print

The goal of testr6print is to show how to modify the printing behaviour of a 
subclass of the `"tbl_df"` class in the tibble package. 
The part that made it work (I believe) was to add the `@importFrom` and `@export`
comments (see the changed tibble print [here](https://github.com/urswilke/testr6print/commit/98f225b68ed3feebc6800830904681b93738ff0a#diff-b11b52486f7c60d184d1d0c3f5ae88135db04d13d209d4be06da37888af2fbb5)).

```
#' @importFrom pillar tbl_sum
#' @export
<method definition here>
```
(see [here](https://github.com/urswilke/testr6print/blob/d95ed8975d857d6c64739b98723ae98431c0723d/R/my_class.R#L52) for instance)

## Installation

You can install the development version of testr6print like so (but it should also be enough to just browse in this git repo).

```{r, eval=FALSE}
devtools::install_github("urswilke/testr6print")
```

## Example

This is a basic example which shows you the modified tibble print of the 
object inheriting from `tbl_df` in a field of the dummy R6 class

```{r}
library(testr6print)
MyClass$new()
```

